%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSkillItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingEnvironmentAndTools}[1]{} %\textbf{Environment/Tools:}{ #1}}


\newcommand{\cplusplus}{C\texttt{++}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Vasavi Aytha}} & Email : \href{mailto:vasavipravallika@gmail.com}{vasavipravallika@gmail.com}\\
  & Mobile : +1-209-782-7284 \\
\end{tabular*}


\begin{comment}
Engineering %age as far as I remeber is 86% (Or is it 76%?). Figure it out when you find time!!
\end{comment}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {G Pulla Reddy College of Engineering and Technology}{Kurnool, India}
      {Bachelor of Engineering in Electrical and Electronics}{Aug. 2007 -- July. 2011}

\begin{comment}
    \resumeSubheading
      {St. Joseph's Primary School}{Kurnool, India}
      {10th Grade}{July. 2005}
\end{comment}


  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}

\begin{comment}
\end{comment}

  \resumeSubHeadingListStart
    \resumeSkillItem{People-oriented}
    \resumeSkillItem{Customer service-oriented}
    \resumeSkillItem{Excellent communication skills}
    \resumeSkillItem{Friendly demeanor}
    \resumeSkillItem{Strong work ethic}
    \resumeSkillItem{Outstanding interpersonal skills}
    \resumeSkillItem{Goal-oriented}
    \resumeSkillItem{Technical aptitude}
  \resumeSubHeadingListEnd

%Authorized to work in the US for any employer

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

   \resumeSubheading
      {Sylvan Learning Academy}{West Des Moines, IA}
      {Coding/Robotics instructor}{Sep 2018 - Present}
      \resumeItemListStart
        \resumeItem{Coding instructor}
	 {Guide students (3rd to 8th grade) help them design games to develop their programming skills using Java and Python scripts on tynker.com platform}
        \resumeItem{Lesson plans}
	 {Creating classes and assigning lessons to the students and maintaining progress on individual basis.}

      \resumeItemListEnd

   \resumeSubheading
      {Cadence Academy}{West Des Moines, IA}
      {Pre-K teacher}{Sep 2017 - Present}
      \resumeItemListStart
        \resumeItem{Kindergarten preparation}
	 {Prepared students for acceleration to Kindergarten through letter and number recognition and age appropriate instruction.}
        \resumeItem{Worksheets}
	 {Regularly made students to complete worksheets designed for Pre-K.}
        \resumeItem{Lesson plans}
	 {Planned prepared and organized daily lesson plans and activities based on common core standards.}
        \resumeItem{Parent communication}
         {Communicated achievements and activities to parents through text notifications and conferences.}
        \resumeItem{Structured learning}
         {Supported students through structured classroom management systems.}

      \resumeItemListEnd
      \resumeSubHeadingEnvironmentAndTools{\cplusplus, JavaScript, Unix(AIX,  HP-UX,  Solaris), RAPID(UI development framework), SQL, ComDB, STL, FIX-protocol, Service orientied architecture, XML, Multithreading (IPC), OOP, svn.}


    \resumeSubheading
      %https://www.toshibatec.com/cnt/products_overseas/MFP/
      {TJMaxx}{Clive, IA}
      {Sales Associate}{July 2017 - July 2018}
      \resumeItemListStart
        \resumeItem{Customer recommendations} 
	{Observed customers and listened closely to questions to ascertain best clothing options and made recommendations accordingly.}
        \resumeItem{Stocking} 
	{Kept clothing racks neatly organized and fully stocked.}
        \resumeItem{Special Orders} 
	{Placed special orders for out of stock items.}
        \resumeItem{Cashier} 
	{Worked as a cashier to cover missing cashiers.}
      \resumeItemListEnd
      \resumeSubHeadingEnvironmentAndTools{\cplusplus, Linux  IPCs,  Multithreading, Windriver  Linux,  PowerPC,  bash  scripting,  PVCS(version control), sqlite-db, awk, sed, valgrind}

    \resumeSubheading
      {Bitla Software}{Bangalore, India}
      {Software Engineer}{May 2011 - Jun 2012}
      \resumeItemListStart
      %RubyOnRails project.
        \resumeItem{Web developement}
          {Develop a product(website) to book bus tickets on RubyOnRails platform.}
      \resumeItemListEnd
      %\resumeSubHeadingEnvironmentAndTools{Matlab, Bluetooth CVSD spec/algorithms, CVS}

  \resumeSubHeadingListEnd

\begin{comment}
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
    \resumeSubItem{Mac Setup}
      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd
\end{comment}

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, \cplusplus, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}


