%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Naveen Gara}} & Email : \href{mailto:naveen.gara@gmail.com}{naveen.gara@gmail.com}\\
  & Mobile : +1-848-628-4207 \\
\end{tabular*}


\begin{comment}
Engineering %age as far as I remeber is 86% (Or is it 76%?). Figure it out when you find time!!
\end{comment}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sri Jayachamarajendra College of Engineering}{Mysore, India}
      {Bachelor of Engineering in Electronics and Communications}{Aug. 2002 -- July. 2006}
  \resumeSubHeadingListEnd


%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages} {C++, C, python, bash}
    \resumeSubItem{Platforms} {Linux(Windriver, Ubuntu), Unix(HP-UX, AIX, Solaris)}
    \resumeSubItem{Tools} {CMake, GNUMake, gdb, }
    \resumeSubItem{Testing Frameworks} {Squish, GoogleTest, Cucumber}
    \resumeSubItem{Protocols} {CAN (Vehicle bus standard), FIX(Financial Information eXchange)}
    \resumeSubItem{Others} {Test Driven Development, Agile, Multithreading, Qt, Mercurial, Git, sqlite, ComDB, Linux IPCs, awk, sed, valgrind}

    
  \resumeSubHeadingListEnd
 


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

\begin{comment}
Some reference links,
John Deere,
https://www.deere.com/en/technology-products/precision-ag-technology/guidance/gen-4-premium-activation/

\end{comment}

    \resumeSubheading
      {John Deere}{Des Moines, IA}
      {Software Engineer}{June 2012 - Present}
      \resumeItemListStart
        \resumeItem{Gen4 CommandCenter\texttrademark\ Displays}
          {Develop software for displays of family of Autotrack guidance agriculture machines (like tractors) which farmers use for Presicion Agriculture. Followed Agile methodologies with Test driven development.}
        \resumeItem{Defects Triaging}
          {Initial triaging/analysing of defects that are logged by farm testers to be assigned to right team. This needs a robust knowledge of the entire system and involves a lot of communication with various teams.}
        \resumeItem{Reprogramming Firmware}
          {Designed and developed Reprogramming module for embedded display which deals with installation and updates of Gen4 CommandCenter Display.}
      \resumeItemListEnd

    \resumeSubheading
      {Bloomberg}{Manhattan, NY}
      {Software Engineer}{Apr 2011 - May 2012}
      \resumeItemListStart
        \resumeItem{STEP (Add on software for OrderManagementSystem)}
          {Service for sending email, push and in-app notifications. Involved in features such as delivery time optimization, tracking, queuing and A/B testing. Built an internal app to run batch campaigns for marketing etc.}
        \resumeItem{Tool to test STEP}
          {Bulk data processing and injection service from Hadoop to Cassandra and provides a thin REST layer on top for serving offline computed data online.}
      \resumeItemListEnd

    \resumeSubheading
      {Toshiba}{Bangalore, India}
      {Software Developer}{Aug 2006 - Feb 2011}
      \resumeItemListStart
        \resumeItem{Printer Firmware}
          {Develop firmware for Toshiba's vast range of Multi Function Peripherals(MFPs) in C++ and WindriverLinux.}
        \resumeItem{Onsite Coordinator}
          {Get involved with architecture team at client location and communicate the requirements to offshore team. Was in this role for about an year.}
        \resumeItem{Integration}
          {Integration of all three layers at the client location (Toshiba, Japan) by coordinating with all the teams.}
        \resumeItem{MFPUtility Libraries}
          {Develop algorithms/libraries specific to printers (like Magnification\%, Drawer selection, ExitTray selection, Staple/Duplex judgment.}
      \resumeItemListEnd

    \resumeSubheading
      {Mindtree}{Bangalore, India}
      {Internship Project}{Dec 2005 - Mar 2006}
      \resumeItemListStart
\begin{comment}
Developing SCILAB model CVSD encoder/decoder for Bluetooth: 
\end{comment}
        \resumeItem{CVSD encode/decoder}
          {Develop SCILAB model for CVSD encoder/decoder (which is an Audio CODEC) as per Bluetooth CVSD specification and do the performance analysis to find the best parameters.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\begin{comment}
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
    \resumeSubItem{Mac Setup}
      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd
\end{comment}

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
